\documentclass[twocolumn, 10.5pt]{article}
\usepackage{verbatim}
\usepackage{amsfonts}
\usepackage{geometry}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amssymb}
\usepackage{listings}
\usepackage{graphicx}
\usepackage{clrscode3e}
\usepackage{txfonts}
\usepackage{fontspec}
\usepackage{ctex}
\setmainfont{Times New Roman}
\geometry{top=2.5cm,bottom=2.5cm,left=2.5cm,right=2.5cm}
\setlength\parindent{0em}
\begin{document}
	\title{Problem Solving Homework (Week 3)}\author{161180162 Xu Zhiming}\maketitle
	\section*{JH Chapter 2}
	\subsection*{3.3.2.7}
		\begin{codebox}
			\zi\proc{Divide-And-Conquer-MVC$(G)$}
			\li Find all strongly connected components with\zi
			Tarjan's algorithm\li 
			Find the minimum vertex cover of each SCC, respectively,\zi
			with the algorithm introduced in {3.3.2.4}\li 
			Combine vertex covers of each SCC\li 
			\Return the global minimum vertex cover 
		\end{codebox}
		\textbf{REVISE: }Modify Step 3 in Algorithm 3.3.2.4 from exhaustive search to divide-and-conquer, i.e., $(G,m)\in VC\iff \left(G_1,m-1)\in VC\right)\lor\left((G_2,m-1)\in VC\right)$.
		\subsection*{3.3.2.8}
	\begin{proof}
		To prove the given statement, It is needed to show that there exists a \emph{Var-parameterized polynomial-time algorithm} for \proc{Max-Sat}. What follows is one of such algorithms. Suppose there are $n$ Boolean functions in such CNF.
		\begin{codebox}
			\zi\proc{Var-Para-For-Max-Sat$(\Phi)$}\li 
			Make all possible assignments for all $\Phi$:\Then\zi
			\Comment{With this assignment, test whether CNF is true} \li 
			\If assignment $\left\{\mathcal{A}_{k_1},\mathcal{A}_{k_2},\cdots,\mathcal{A}_{k_n}\right\}$ for\zi $\left\{\Phi_1,\Phi_2,\cdots,\Phi_n \right\}$ satisfies CNF
			\Then\li \Return\const{true}
			\End\End\li\Return\const{false}
		\end{codebox} 
	\end{proof}
	Since it has tested all possible assignments, and will return true if such CNF can be satisfied, yield false, otherwise. It solves the problem. Then, we prove it to be \emph{Var-parameterized polynomial-time} where $Var(\Phi_i)$ is the variables occurring in $\Phi_i$. The time complexity for test a series of assignments in line 2 is $O(n)$. However, line 1 will run $$\sum_{i=1}^{n}2^{Var\left(\Phi_i\right)}$$ times. Hence the total running time is $$O\left(n\cdot\sum_{i=1}^{n}2^{Var(\Phi_i)}\right)=O\left(n^2\cdot 2^{\max\left(Var(\Phi_i)\right)}\right).$$Therefore, \proc{Max-Sat} is fixed-parameterized polynomial-time tractable according to \emph{Var}.
	\subsection*{3.3.2.9}
	\begin{codebox}
		\li\proc{Max-Set-Cover$(X,F,k)$}\li 
		Set $T\gets\emptyset$ and $C\gets \emptyset$\li 
		\If $|T| < k$and $|C| < p + \Delta − 1$ \li 
		\Then Pick a set $S_i \in S \backslash T $ that covers the largest \zi number of elements in
		$X \backslash C$\li 
		Branch on \proc{Max-Set-Cover$(T\cap \{S_i\}, C\cap S_i)$} and, \zi $\forall x\in S_i \backslash C$ branch on \proc{Max-Set-Cover$(T, C \cap \{x\})$}\li 
		\Else\li  
		\If  $|T| = k$\li \Then Store $T$\li 
		\Else\li 
		$(|C| = p + \Delta − 1)$ store a solution covering $C$\zi (if possible)\End\End\li 
		Output the best among solutions stored
	\end{codebox}
	\textbf{REVISED: }Set cover problem. $Pot(X)$ is the set of all subsets of the set $X$. Similar to \proc{VCP}, use divide-and-conquer.\par 
	Divide: $((X_i,F_i),k-1)$: Select any $S_i\in F$. Let $X_i=X\backslash S_i,F_i=f(F,i)$, function $f$ deletes $S_i$ and all elements of $S_i$ in $S_1,\cdots,S_{i-1},S_{i+1},\cdots, S_l$. Using induction, $((X_T,F_T),0)$ is trivial. Complexity is $O(Pat^{pat}|X|)$.
	\subsection*{真·多项式时间的最大流算法}
	\textbf{REVISE NOTE: }Push relabel in CLRS\par 
	前置重贴标签算法在任何流网络上的运行时间都为$O(V^3)$。因为每个节点的重贴标签操作数不会超过$O(V)$，而所有节点的重贴标签操作总次数不会超过$O(V^2)$。算法花在重贴标签上的时间不会超过$O(VE)$，饱和推送的总次数为$O(VE)$。综合可得，复杂度为$$O(V^3+VE)=O(V^3).$$
\end{document}